---
title: "w241 Final Project"
author: "Cendy Lin"
date: "April 22, 2017"
output: html_document
---

## Load Packages
```{r}
library(ggplot2)
library(reshape2)
library(car)
library(stargazer)
library(lmtest)
library(sandwich)
library(foreign)
library(multiwayvcov)
```

## Prepare Data
```{r}
data = read.csv("./data.csv") #uncoded dataframe
d = data # coded dataframe

# view columns
names(d)

# drop username row for anonimity
d = d[,-1]

# encode gender (male = 1, female = 0)
d$male = 1
d$male[d$gender == "Female"] = 0

# encode age (<44 = 1, >44 = 0)
d$age_code = 1
d$age_code[d$age == "45-54" | d$age == "55-64"] = 0

# encode OS (Apple = 1, Other = 0)
d$apple = 1
d$apple[grep("Android", d$os)] = 0 # regex, if contains 'Android', encode as 1
d$apple[d$os == "Blackberry"] = 0

# encode num_phones (personal use phone = 0, work & personal phone = 1)
d$personal_phone = 0
d$personal_phone[grep("only", d$num_phones)] = 1

# encode phone_use (at least once an hour = 1, less than once an hour = 0)
d$phone_usage = 1
d$phone_usage[grep("4", d$phone_use)] = 0 # regex, if contains '4', encode as 1

# encode relationship (friend/fam = 1, other = 0)
d$relation = 1
d$relation[d$relationship == ""] = 0

# label treat as treatment/control
d$treat_group = "treatment"
d$treat_group[d$treat == 0] = "control"

# drop columns
d = d[,c(-2, -6, -7, -8 ,-9, -10, -11, -12)]

# reorder columns so stress observations on the right
d = d[c("id", "treat", "full_attrit", "block", "treat_group", "male", "age_code", "apple", "personal_phone",
     "phone_usage", "relation", "c1", "c2", "c3", "c4", "c5", "c6", "c7",
     "b1", "b2", "b3", "b4", "b5", "b6", "b7", 
     "t1", "t2", "t3", "t4", "t5", "t6", "t7")]

# change column names 
colnames(d) <- c("id", "treat_code", "attrit", "block", "treat_group", "male", "age", "apple", 
                  "personal_phone","phone_use", "relationship", "c1", "c2", "c3", 
                  "c4", "c5", "c6", "c7", "b1", "b2", "b3", "b4", "b5", "b6", 
                  "b7", "t1", "t2", "t3", "t4", "t5", "t6", "t7")

sum(d$treat_code == 0) #38 in control
sum(d$treat_code == 1) #39 in treatment

# dataframe for non-attritors
df = d[d$attrit == 0,]
nrow(df)
```

Codes:
* comply: comply=1, non-comply=0 for treatment group only 
* male: male=1, female=0
* age: <44=0, >44=1
* apple: apple=1, other=0 
* phone_usage: at least once an hour=0, less than once an hour=1 
* peronal_phone: personal use phone = 0, work & personal phone = 1
* relation: friend/fam=0, other=1

### Reshape into indivdual observations by day
```{r}
df2 = melt(df, id.var = c("id", "treat_code", "attrit", "block", "treat_group", "male", "age", "apple", 
                  "personal_phone","phone_use", "relationship", "c1", "c2", "c3", 
                  "c4", "c5", "c6", "c7"), variable.name = "day")

# recode 'day' column as number day
index = levels(df2$day)
values = c(1:14)
df2$day = values[match(df2$day, index)]

# reformat compliance columns
df2$comply = NA
a = which(df2$day == 8)
df2$comply[a] = df2$c1[a] # turns into factor
b = which(df2$day == 9)
df2$comply[b] = df2$c2[b] 
c = which(df2$day == 10)
df2$comply[c] = df2$c3[c]
e = which(df2$day == 11)
df2$comply[e] = df2$c4[e]
f = which(df2$day == 12)
df2$comply[f] = df2$c5[f]
g = which(df2$day == 13)
df2$comply[g] = df2$c6[g]
h = which(df2$day == 14)
df2$comply[h] = df2$c7[h]
head(df2)
# drop c1-c7, rename 'value' to 'stress'
df2 = df2[,c(-12, -13, -14, -15, -16, -17, -18)]
colnames(df2)[13] <- "stress"

sum(df2$treat_code == 0) # 350 or 25*14 control obs (baseline and treatment week) 
sum(df2$treat_code == 1) # 434 or 31*14 treatment obs (baseline and treatment week)

```

## Exploratory Analysis on Restricted Subject Pool
```{r}
# Age and Gender
d2 = data[data$full_attrit == 0,]

# label treat as treatment/control
d2$treat_group = "treatment"
d2$treat_group[d2$treat == 0] = "control"

position = c("Under 18", "18-24", "25-34", "35-44", "45-54", "55-64")
ggplot(data.frame(d2$age), aes(x=d2$age, fill = d2$gender)) + 
  geom_bar(position="dodge") + 
  scale_x_discrete(limits = position) + 
  ggtitle("Age Distribution by Gender") + 
  labs(x="Age Bin")

# Age and Treatment Group
ggplot(data.frame(d2$age), aes(x=d2$age, fill = d2$treat_group)) + 
  geom_bar(position="dodge") + 
  scale_x_discrete(limits = position) + 
  ggtitle("Age Distribution by Treatment Group") + 
  labs(x="Age Bin")

```

## Covariate balance check on restricted subject pool
```{r}
# Not using individual observations

# gender
t.test(df$male ~ df$treat_code, var.equal=F) # not significant

# age
t.test(df$age ~ df$treat_code, var.equal=F) # not significant

# apple
t.test(df$apple ~ df$treat_code, var.equal=F) # not significant

# personal phone
t.test(df$personal_phone ~ df$treat_code, var.equal=F) # not significant

# phone use
t.test(df$phone_use ~ df$treat_code, var.equal=F) # not significant

# relationship
t.test(df$relationship ~ df$treat_code, var.equal=F) # not significant

# Check with F-test on restricted subject pool
mod.null <- glm(treat_code ~ 1, family = "binomial", data = df)
mod      <- glm(treat_code ~ 1 + male + age + relationship + apple + personal_phone + phone_use, 
                family = "binomial", data = df)
anova(mod.null, mod, test = "LRT")


```

## Analysis on "full" attritors
```{r}
full_attrit = d[d$attrit == 1,]
nrow(full_attrit)

names(full_attrit)
sum(full_attrit$treat_code == 1)
sum(full_attrit$treat_code == 0)

# correlation against all 
cor(d$attrit, d$treat_code)
cor(d$attrit, d$male)
cor(d$attrit, d$age)
cor(d$attrit, d$apple)
cor(d$attrit, d$personal_phone)
cor(d$attrit, d$phone_use)
cor(d$attrit, d$relationship)

d_treat = d[d$treat_code == 1,]
d_contr = d[d$treat_code == 0,]

# correlation against control
cor(d_contr$attrit, d_contr$male)
cor(d_contr$attrit, d_contr$age)
cor(d_contr$attrit, d_contr$apple)
cor(d_contr$attrit, d_contr$personal_phone)
cor(d_contr$attrit, d_contr$phone_use)
cor(d_contr$attrit, d_contr$relationship)

# correlation against treatment
cor(d_treat$attrit, d_treat$male)
cor(d_treat$attrit, d_treat$age)
cor(d_treat$attrit, d_treat$apple)
cor(d_treat$attrit, d_treat$personal_phone)
cor(d_treat$attrit, d_treat$phone_use)
cor(d_treat$attrit, d_treat$relationship)

# gender
t.test(full_attrit$male ~ full_attrit$treat_code, var.equal=F) # not significant

# age
t.test(df$age ~ df$treat_code, var.equal=F) # not significant

# apple
t.test(df$apple ~ df$treat_code, var.equal=F) # not significant

# personal phone
t.test(df$personal_phone ~ df$treat_code, var.equal=F) # not significant

# phone use
t.test(df$phone_use ~ df$treat_code, var.equal=F) # not significant

# relationship
t.test(df$relationship ~ df$treat_code, var.equal=F) # not significant
```

## Initial DiD Analysis - ignoring attrition
```{r}
# create rows for difference-in-difference
baseline = df2[df2$day < 8,]
treatment = df2[df2$day > 7,]
did = treatment$stress - baseline$stress

# Build dataframe with DiD as outcome only
treat = df2[c(1:length(did)),]$treat_group
treat_code = df2[c(1:length(did)),]$treat_code
id = df2[c(1:length(did)),]$id
block = df2[c(1:length(did)),]$block
age = df2[c(1:length(did)),]$age
day = df2[c(1:length(did)),]$day
rel = df2[c(1:length(did)),]$relationship
male = df2[c(1:length(did)),]$male
apple = df2[c(1:length(did)),]$apple
pers = df2[c(1:length(did)),]$personal_phone
use = df2[c(1:length(did)),]$phone_use

diff = data.frame(id, treat, treat_code, block, age, rel, male, apple, pers, use, day, did)

# create weekday column for plotting
diff$weekday = "Monday"
diff[diff$day == 2,]$weekday = "Tuesday"
diff[diff$day == 3,]$weekday = "Wednesday"
diff[diff$day == 4,]$weekday = "Thursday"
diff[diff$day == 5,]$weekday = "Friday"
diff[diff$day == 6,]$weekday = "Saturday"
diff[diff$day == 7,]$weekday = "Sunday"

# % of total missing DiD observations
sum(is.na(diff$did))/nrow(diff)

# count of NA in treatment groups
sum(is.na(diff$did[diff$treat == "control"])) #38
sum(is.na(diff$did[diff$treat == "treatment"])) #61

# % NA DiD in control and treatment
38/sum(diff$treat == "control")
61/sum(diff$treat == "treatment")

# distribution by treatment group
ggplot(data.frame(diff$did), aes(x=diff$did, fill = diff$treat)) + 
  geom_bar(position="dodge") + 
  ggtitle("Distribution of Change in Stress Levels") + 
  labs(x="Change in Stress", fill="")

# boxplot by treatment group
ggplot(data.frame(diff$did), aes(x=diff$treat, y=diff$did, fill=diff$treat)) + 
  geom_boxplot() + 
  ggtitle("Difference Stress Levels") + 
  labs(x="Stress DiD")

# model ignoring attrition and no clusters on ID
m1_wrong = lm(did ~ treat + weekday, data=diff)

# model WITH clusters on ID but ignoring attrition
m1_wrong$cluster.vcov = cluster.vcov(m1_wrong, ~ id)
m1 = coeftest(m1_wrong, m1_wrong$cluster.vcov)
m1

# model ignoring attrition and using fixed effects by individual ID
# m2 = lm(did ~ treat + weekday + factor(id), data = diff)

#m2$cluster.vcov = cluster.vcov(m2, ~ id)
#m2a = coeftest(m2, m2$cluster.vcov)

# Compare models
#stargazer(m1, m2, type="text", omit = "id",
#          dep.var.labels.include = FALSE,
#          add.lines = list(c("Fixed effects?", "No", "Yes"),
#          column.labels   = c("Clustered SE", "Fixed Effects")))
```

## Analyzing non-compliance
```{r}
# Number non-compliance in treatment group
nc = sum(df2[df2$treat_code == 1 ,]$comply==0, na.rm=TRUE)

# Total Number of non-missing treatment responses in treatment week
t = sum(df2$treat_code == 1 & df2$day > 7 & !is.na(df2$stress))

# % of noncompliance
nc/t

# alpha 
1-nc/t
```


## Analyzing Attrition
```{r}
# %Attrition in each treatment group
sum(is.na(diff[diff$treat=="treatment",]$did)) #28 attrited DiD responses in treatment
mean(is.na(diff[diff$treat=="control",]$did)) # 22% attrited DiD responses in conttrol
mean(is.na(diff$did)) #25% attrited responses overall

# create attrition column to tag attrition for plotting
diff$attrit = 0
diff[is.na(diff$did),]$attrit = 1
nrow(diff)

# Get counts by day
diffplot = data.frame(table(diff$weekday, diff$treat, diff$attrit))
diffplot = diffplot[diffplot$Var3==1,] # get only rows with attrition

# distribution of attrition by treatment group
label_pos = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
ggplot(diffplot,aes(Var1,Freq,fill=Var2)) +
  geom_bar(stat="identity",position='dodge') +
  scale_x_discrete(limits=label_pos) +
  ggtitle("Attrited DiD Distribution by Treatment Group") +
  labs(x="Weekday")

# correlation against all 
cor(diff$attrit, diff$treat_code)
cor(diff$attrit, diff$male)
cor(diff$attrit, diff$age)
cor(diff$attrit, diff$apple)
cor(diff$attrit, diff$pers)
cor(diff$attrit, diff$use)
cor(diff$attrit, diff$rel)
cor(diff$attrit, diff$day)

diff_treat = diff[diff$treat_code == 1,]
diff_contr = diff[diff$treat_code == 0,]

# correlation against control
cor(diff_contr$attrit, diff_contr$male)
cor(diff_contr$attrit, diff_contr$age)
cor(diff_contr$attrit, diff_contr$apple)
cor(diff_contr$attrit, diff_contr$pers)
cor(diff_contr$attrit, diff_contr$use)
cor(diff_contr$attrit, diff_contr$rel)
cor(diff_contr$attrit, diff_contr$day)

# correlation against treatment
cor(diff_treat$attrit, diff_treat$male)
cor(diff_treat$attrit, diff_treat$age)
cor(diff_treat$attrit, diff_treat$apple)
cor(diff_treat$attrit, diff_treat$pers)
cor(diff_treat$attrit, diff_treat$use)
cor(diff_treat$attrit, diff_treat$rel)
cor(diff_treat$attrit, diff_treat$day)

```

## Dealing with Attrition: Max ATE
```{r}
minstress = min(df2$stress, na.rm=TRUE) #1
maxstress = max(df2$stress, na.rm=TRUE) #5

# Max Effect, 
# control to have +4 DiD - baseline:1, treatment: 5
# treatment to have -4 DiD - baseline: 5, treatment 1

df2$maxstress = df2$stress

# control
df2[df2$day<8 & df2$treat_code == 0,]$maxstress[is.na(df2[df2$day<8 & df2$treat_code == 0,]$stress)] = minstress
df2[df2$day>7 & df2$treat_code == 0,]$maxstress[is.na(df2[df2$day>7 & df2$treat_code == 0,]$stress)] = maxstress

# treatment
df2[df2$day<8 & df2$treat_code == 1,]$maxstress[is.na(df2[df2$day<8 & df2$treat_code == 1,]$stress)] = maxstress
df2[df2$day>7 & df2$treat_code == 1,]$maxstress[is.na(df2[df2$day>7 & df2$treat_code == 1,]$stress)] = minstress

# create rows for difference-in-difference
baseline = df2[df2$day < 8,]
treatment = df2[df2$day > 7,]
max_did = treatment$maxstress - baseline$maxstress

# Build dataframe with DiD as outcome only
max_diff = diff[,c(1:11, 13:14)]
max_diff$max_did = max_did

# distribution by treatment group
ggplot(data.frame(max_diff$max_did), aes(x=max_diff$max_did, fill = max_diff$treat)) + 
  geom_bar(position="dodge") + 
  ggtitle("Distribution of Change in Stress Levels (Max Effect)") + 
  labs(x="Change in Stress", fill="") +
  scale_x_discrete(limits=c(-4:4))

# boxplot by treatment group
ggplot(data.frame(max_diff$max_did), aes(x=max_diff$treat, 
                                         y=max_diff$max_did, 
                                         fill=max_diff$treat)) + 
  geom_boxplot() + 
  ggtitle("Difference in Difference of Stress Levels by Day of Week") + 
  labs(x="Group", y="DiD Stress")

# Difference in means 
mean(max_diff[max_diff$treat == "treatment",]$max_did) - 
  mean(max_diff[max_diff$treat == "control",]$max_did)

# max effect model ignoring clustered SEs
max1_wrong = lm(max_did ~ treat + weekday, data=max_diff)
summary(max1_wrong)

# max effect model with clustered SEs
max1_wrong$cluster.vcov = cluster.vcov(max1_wrong, ~ id)
max1 = coeftest(max1_wrong, max1_wrong$cluster.vcov)
max1

# max effect model with fixed effects by individual ID
#max2 = lm(max_did ~ treat + weekday + factor(id), data = max_diff)
#summary(max2)

#max2$cluster.vcov = cluster.vcov(max2, ~ id)
#max2a = coeftest(max2, max2$cluster.vcov)
#max2a

# Compare models
#stargazer(max1, max2, max2a, type="text", omit = "id",
#          dep.var.labels.include = FALSE,
#          add.lines = list(c("Individual fixed effects?", "No", "Yes", "Yes"),
#                           c("Clustered SE?", "Yes", "No", "Yes")),
#          column.labels   = c("Clustered SE", "Fixed Effects", "Both"))

```

## Dealing with Attrition: Min ATE
```{r}
minstress = min(df2$stress, na.rm=TRUE) #1
maxstress = max(df2$stress, na.rm=TRUE) #5

# Max Effect, 
# control to have -4 DiD - baseline week:5, treatment: 1
# treatment to have +4 DiD - baseline week: 1, treatment 5

df2$minstress = df2$stress

# control
df2[df2$day<8 & df2$treat_code == 0,]$minstress[is.na(df2[df2$day<8 & df2$treat_code == 0,]$stress)] = maxstress
df2[df2$day>7 & df2$treat_code == 0,]$minstress[is.na(df2[df2$day>7 & df2$treat_code == 0,]$stress)] = minstress

# treatment
df2[df2$day<8 & df2$treat_code == 1,]$minstress[is.na(df2[df2$day<8 & df2$treat_code == 1,]$stress)] = minstress
df2[df2$day>7 & df2$treat_code == 1,]$minstress[is.na(df2[df2$day>7 & df2$treat_code == 1,]$stress)] = maxstress

# create rows for difference-in-difference
baseline = df2[df2$day < 8,]
treatment = df2[df2$day > 7,]
min_did = treatment$minstress - baseline$minstress

# Build dataframe with DiD as outcome only
min_diff = diff[,c(1:11, 13:14)]
min_diff$min_did = min_did

# distribution by treatment group
ggplot(data.frame(min_diff$min_did), aes(x=min_diff$min_did, fill = min_diff$treat)) + 
  geom_bar(position="dodge") + 
  ggtitle("Distribution of Change in Stress Levels (Min Effect)") + 
  labs(x="Change in Stress", fill="") +
  scale_x_discrete(limits=c(-4:4))

# boxplot by treatment group
ggplot(data.frame(min_diff$min_did), aes(x=min_diff$treat, 
                                         y=min_diff$min_did, 
                                         fill=min_diff$treat)) + 
  geom_boxplot() + 
  ggtitle("Difference in Difference of Stress Levels by Group") + 
  labs(x="Group", y="DiD Stress")

# Difference in means 
mean(min_diff[min_diff$treat == "treatment",]$min_did) - 
  mean(min_diff[min_diff$treat == "control",]$min_did)

# max effect model ignoring clustered SEs
min1_wrong = lm(min_did ~ treat + weekday, data=min_diff)

# max effect model with clustered SEs
min1_wrong$cluster.vcov = cluster.vcov(min1_wrong, ~ id)
min1 = coeftest(min1_wrong, min1_wrong$cluster.vcov)
min1

# max effect model with fixed effects by individual ID
#min2 = lm(min_did ~ treat+ factor(id), data = min_diff)
#summary(min2)

#min2$cluster.vcov = cluster.vcov(min2, ~ id)
#min2a = coeftest(min2, min2$cluster.vcov)
#min2a

# Compare models
stargazer(m1, max1, min1, type="text", 
          column.labels   = c("Ignore Attrition", "Max Effect", "Min Effect"))

```

