---
title: "Amazon Gift Card Raffle"
author: "Andrew Lam"
date: "4/19/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load packages
library(data.table)
```

```{r}
set.seed(1590)
```

The purpose of this file is to document the giveaway of five $100 Amazon gift cards.

Eligibility requirements:

"In order to be eligible for the Amazon Gift Card Raffle, you must complete >90% of these daily surveys and do so within 24 hours of it being emailed to you. Individuals who respond to 100% of the surveys will receive two entries. So, the more you respond the higher your chances of winning!"

```{r}
# Calculation of number of responses needed to qualify for raffle (i.e., >90% response rate)

# For subjects in pilot
21 * 0.9

# For subjects in experiment
14 * 0.9
```

```{r}
# Load data
ds1 <- read.csv("./DS1 - Treatment Group Post Treatment Survey.csv")
ds1 <- data.table(ds1)

ds2 <- read.csv("./DS2 - Control Group Post Treatment Survey.csv")
ds2 <- data.table(ds2)

ds3 <- read.csv("./DS3 - Baseline Survey (Both Groups).csv")
ds3 <- data.table(ds3)
```

```{r}
# Initial look at data 
head(ds1)
colnames(ds1)
```

```{r}
# Initial look at data 
head(ds2)
colnames(ds2)
```

```{r}
# Initial look at data 
head(ds3)
colnames(ds3)
```

```{r}
# Only keeping "Timestamp" and "Username" columns
ds1 <- ds1[ , c("Timestamp", "Username")]
ds2 <- ds2[ , c("Timestamp", "Username")]
ds3 <- ds3[ , c("Timestamp", "Username")]
```

```{r}
# Merging data
d <- rbind(ds1, ds2, ds3)
```

```{r}
# Counting number of responses per subject
d <- d[ , Counts := .N, by = "Username"]
```

```{r}
# Subset on unique rows
d <- unique(d, by="Username")
```

```{r}
# Write to CSV
write.csv(d, "Amazon Gift Card Raffle.csv")
```

Since we're using "Username" (the subject's email address) as the identifier, and some subjects misspelled their email addresses in the daily surveys, I need to manually spot check and combine certain rows.  Afterward, I will calculate the number of entries for each subject, create a row for each entry, and number each row.  Finally, I will select 5 ID numbers from 1 to 57 (57 being the total number of entries).

```{r}
# Winning IDs 
sample(1:57, size=5, replace=FALSE)
```
