---
title: "w241 Final Project"
author: "Cendy Lin"
date: "April 22, 2017"
output: html_document
---

## Load Packages
```{r}
library(ggplot2)
library(reshape2)
library(car)
library(stargazer)
library(lmtest)
library(sandwich)
library(foreign)
library(multiwayvcov)
```

## Prepare Data
```{r}
data = read.csv("./data.csv")

# Remove "full attritors" where we have no treatment
df = data[data$full_attrit==0,]

# view columns
names(df)

# drop username row for anonimity
df = df[,-1]

# encode gender (male = 1, female = 0)
df$male = 1
df$male[df$gender == "Female"] = 0

# encode age (<44 = 1, >44 = 0)
df$age_code = 1
df$age_code[df$age == "45-54" | df$age == "55-64"] = 0

# encode OS (Apple = 1, Other = 0)
df$apple = 1
df$apple[grep("Android", df$os)] = 0 # regex, if contains 'Android', encode as 1
df$apple[df$os == "Blackberry"] = 0

# encode num_phones (personal use phone = 0, work & personal phone = 1)
df$personal_phone = 0
df$personal_phone[grep("only", df$num_phones)] = 1

# encode phone_use (at least once an hour = 1, less than once an hour = 0)
df$phone_usage = 1
df$phone_usage[grep("4", df$phone_use)] = 0 # regex, if contains '4', encode as 1

# encode relationship (friend/fam = 1, other = 0)
df$relation = 1
df$relation[df$relationship == ""] = 0

# label treat as treatment/control
df$treat_group = "treatment"
df$treat_group[df$treat == 0] = "control"

# drop columns
df = df[,c(-2, -4, -5, -6, -7, -8 ,-9, -10, -11, -12)]

# reorder columns so stress observations on the right
df = df[c("id", "treat", "treat_group", "male", "age_code", "apple", "personal_phone",
     "phone_usage", "relation", "c1", "c2", "c3", "c4", "c5", "c6", "c7",
     "b1", "b2", "b3", "b4", "b5", "b6", "b7", 
     "t1", "t2", "t3", "t4", "t5", "t6", "t7")]

# change column names 
colnames(df) <- c("id", "treat_code", "treat_group", "male", "age", "apple", 
                  "personal_phone","phone_use", "relationship", "c1", "c2", "c3", 
                  "c4", "c5", "c6", "c7", "b1", "b2", "b3", "b4", "b5", "b6", 
                  "b7", "t1", "t2", "t3", "t4", "t5", "t6", "t7")

sum(df$treat_code == 0) #25 in control
sum(df$treat_code == 1) #31 in treatment
```

Codes:
* comply: comply=1, non-comply=0 for treatment group only 
* male: male=1, female=0
* age: <44=0, >44=1
* apple: apple=1, other=0 
* phone_usage: at least once an hour=0, less than once an hour=1 
* peronal_phone: personal use phone = 0, work & personal phone = 1
* relation: friend/fam=0, other=1

### Reshape into indivdual observations by day
```{r}
df2 = melt(df, id.var = c("id", "treat_code", "treat_group", "male", "age", "apple", 
                  "personal_phone","phone_use", "relationship", "c1", "c2", "c3", 
                  "c4", "c5", "c6", "c7"), variable.name = "day")
# recode 'day' column as number day
index = levels(df2$day)
values = c(1:14)
df2$day = values[match(df2$day, index)]
df2$day
# reformat compliance columns
df2$comply = NA
a = which(df2$day == 8)
df2$comply[a] = df2$c1[a] # turns into factor
b = which(df2$day == 9)
df2$comply[b] = df2$c2[b] 
c = which(df2$day == 10)
df2$comply[c] = df2$c3[c]
d = which(df2$day == 11)
df2$comply[d] = df2$c4[d]
e = which(df2$day == 12)
df2$comply[e] = df2$c5[e]
f = which(df2$day == 13)
df2$comply[f] = df2$c6[f]
g = which(df2$day == 14)
df2$comply[g] = df2$c7[g]

# drop c1-c7, rename 'value' to 'stress'
df2 = df2[,c(-10, -11, -12, -13, -14, -15, -16)]
colnames(df2)[11] <- "stress"

head(df2)
nrow(df2)

sum(df2$treat_code == 0) # control obs (baseline and treatment week)
sum(df2$treat_code == 1) # treatment obs (baseline and treatment week)

```

## Exploratory Analysis of Participants
```{r}
# Age and Gender
d2 = data[data$full_attrit == 0,]

# label treat as treatment/control
d2$treat_group = "treatment"
d2$treat_group[d2$treat == 0] = "control"

position = c("Under 18", "18-24", "25-34", "35-44", "45-54", "55-64")
ggplot(data.frame(d2$age), aes(x=d2$age, fill = d2$gender)) + 
  geom_bar(position="dodge") + 
  scale_x_discrete(limits = position) + 
  ggtitle("Age Distribution by Gender") + 
  labs(x="Age Bin")

# Age and Treatment Group
ggplot(data.frame(d2$age), aes(x=d2$age, fill = d2$treat_group)) + 
  geom_bar(position="dodge") + 
  scale_x_discrete(limits = position) + 
  ggtitle("Age Distribution by Treatment Group") + 
  labs(x="Age Bin")

```

## Covariate balance check
```{r}
# Not using individual observations

# gender
t.test(df$male ~ df$treat_code, var.equal=F) # not significant

# age
t.test(df$age ~ df$treat_code, var.equal=F) # not significant

# apple
t.test(df$apple ~ df$treat_code, var.equal=F) # not significant

# personal phone
t.test(df$personal_phone ~ df$treat_code, var.equal=F) # not significant

# phone use
t.test(df$phone_use ~ df$treat_code, var.equal=F) # not significant

# relationship
t.test(df$relationship ~ df$treat_code, var.equal=F) # not significant

```

## Initial DiD Analysis - ignoring attrition
```{r}
# create rows for difference-in-difference
baseline = df2[df2$day < 8,]
treatment = df2[df2$day > 7,]
did = treatment$stress - baseline$stress

# Build dataframe with DiD as outcome only
treat = df2[c(1:length(did)),]$treat_group
treat_code = df2[c(1:length(did)),]$treat_code
id = df2[c(1:length(did)),]$id
age = df2[c(1:length(did)),]$age
day = df2[c(1:length(did)),]$day
rel = df2[c(1:length(did)),]$relationship
male = df2[c(1:length(did)),]$male
apple = df2[c(1:length(did)),]$apple
pers = df2[c(1:length(did)),]$personal_phone
use = df2[c(1:length(did)),]$phone_use

diff = data.frame(id, treat, treat_code, age, rel, male, apple, pers, use, day, did)

# count of NA differences in treatment groups
sum(is.na(diff$did[diff$treat == "control"])) #38
sum(is.na(diff$did[diff$treat == "treatment"])) #61

# Number of Difference-in-Difference Observations
nrow(diff)

# % NA DiD in control and treatment
38/sum(diff$treat == "control")
61/sum(diff$treat == "treatment")

# distribution by treatment group
ggplot(data.frame(diff$did), aes(x=diff$did, fill = diff$treat)) + 
  geom_bar(position="dodge") + 
  ggtitle("Difference in Difference of Stress Levels by Day of Week") + 
  labs(x="Stress DiD")

# boxplot by treatment group
ggplot(data.frame(diff$did), aes(x=diff$treat, y=diff$did, fill=diff$treat)) + 
  geom_boxplot() + 
  ggtitle("Difference in Difference of Stress Levels by Day of Week") + 
  labs(x="Stress DiD")

# model ignoring attrition and no clusters on ID
m1_wrong = lm(did ~ treat, data=diff)

# model WITH clusters on ID but ignoring attrition
m1_wrong$cluster.vcov = cluster.vcov(m1_wrong, ~ id)
m1 = coeftest(m1_wrong, m1_wrong$cluster.vcov)

# model ignoring attrition and using fixed effects by individual ID
m2 = lm(did ~ treat + factor(id), data = diff)

m2$cluster.vcov = cluster.vcov(m2, ~ id)
m2a = coeftest(m2, m2$cluster.vcov)

# Compare models
stargazer(m1, m2, m2a, type="text", omit = "id",
          dep.var.labels.include = FALSE,
          add.lines = list(c("Fixed effects?", "No", "Yes", "Yes"),
                           c("Clustered SE?", "Yes", "No", "Yes")),
          column.labels   = c("Clustered SE", "Fixed Effects", "Both"))

nrow(diff) - sum(is.na(diff$did))

# Non-compliance? sum non-comply over total treatment observations
sum(df2[df2$treat_code == 1,]$comply==0, na.rm=TRUE)/nrow(df2[df2$treat_code==1,])

mean(is.na(diff[diff$treat=="treatment",]$did)) #28 attrited DiD responses in treatment
mean(is.na(diff[diff$treat=="control",]$did)) # 22% attrited DiD responses in conttrol
mean(is.na(diff$did)) #25% attrited DiD responses
```

## Analyzing Attrition
```{r}
# create attrition column to tag attrition for plotting
diff$attrit = 0
diff[is.na(diff$did),]$attrit = 1

# create weekday column for plotting
diff$weekday = "Monday"
diff[diff$day == 2,]$weekday = "Tuesday"
diff[diff$day == 3,]$weekday = "Wednesday"
diff[diff$day == 4,]$weekday = "Thursday"
diff[diff$day == 5,]$weekday = "Friday"
diff[diff$day == 6,]$weekday = "Saturday"
diff[diff$day == 7,]$weekday = "Sunday"

# Get counts by day
diffplot = data.frame(table(diff$weekday, diff$treat, diff$attrit))
diffplot = diffplot[diffplot$Var3==1,] # get only rows with attrition

# distribution of attrition by treatment group
label_pos = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
ggplot(diffplot,aes(Var1,Freq,fill=Var2)) +
  geom_bar(stat="identity",position='dodge') +
  scale_x_discrete(limits=label_pos) +
  ggtitle("Attrited DiD Distribution by Treatment Group") +
  labs(x="Weekday")

# Check t-test of difference in attrited responses
t.test(diff$attrit ~ diff$treat, var.equal=F) # not significant

# Check with F-test on full responses only
diff_obs = diff[diff$attrit == 0,]

mod.null <- glm(treat_code ~ 1, family = "binomial", data = diff_obs)
mod      <- glm(treat_code ~ 1 + male + age + rel + apple + pers + use, family = "binomial", data = diff_obs)
anova(mod.null, mod, test = "LRT")

```

## Dealing with Attrition: Max ATE
```{r}
minstress = min(df2$stress, na.rm=TRUE) #1
maxstress = max(df2$stress, na.rm=TRUE) #5

# Max Effect, 
# control to have +4 DiD - baseline:1, treatment: 5
# treatment to have -4 DiD - baseline: 5, treatment 1

df2$maxstress = df2$stress

# control
df2[df2$day<8 & df2$treat_code == 0,]$maxstress[is.na(df2[df2$day<8 & df2$treat_code == 0,]$stress)] = minstress
df2[df2$day>7 & df2$treat_code == 0,]$maxstress[is.na(df2[df2$day>7 & df2$treat_code == 0,]$stress)] = maxstress

# treatment
df2[df2$day<8 & df2$treat_code == 1,]$maxstress[is.na(df2[df2$day<8 & df2$treat_code == 1,]$stress)] = maxstress
df2[df2$day>7 & df2$treat_code == 1,]$maxstress[is.na(df2[df2$day>7 & df2$treat_code == 1,]$stress)] = minstress

# create rows for difference-in-difference
baseline = df2[df2$day < 8,]
treatment = df2[df2$day > 7,]
max_did = treatment$maxstress - baseline$maxstress

# Build dataframe with DiD as outcome only
max_diff = diff[,c(1:10, 13)]
max_diff$max_did = max_did

# distribution by treatment group
ggplot(data.frame(max_diff$max_did), aes(x=max_diff$max_did, fill = max_diff$treat)) + 
  geom_bar(position="dodge") + 
  ggtitle("Difference in Difference of Stress Levels by Day of Week") + 
  labs(x="Stress DiD")

# boxplot by treatment group
ggplot(data.frame(max_diff$max_did), aes(x=max_diff$treat, 
                                         y=max_diff$max_did, 
                                         fill=max_diff$treat)) + 
  geom_boxplot() + 
  ggtitle("Difference in Difference of Stress Levels by Day of Week") + 
  labs(x="Group", y="DiD Stress")

# Difference in means 
mean(max_diff[max_diff$treat == "treatment",]$max_did) - 
  mean(max_diff[max_diff$treat == "control",]$max_did)

# max effect model ignoring clustered SEs
max1_wrong = lm(max_did ~ treat + weekday, data=max_diff)
summary(max1_wrong)

# max effect model with clustered SEs
max1_wrong$cluster.vcov = cluster.vcov(max1_wrong, ~ id)
max1 = coeftest(max1_wrong, max1_wrong$cluster.vcov)
max1

# max effect model with fixed effects by individual ID
max2 = lm(max_did ~ treat + weekday + factor(id), data = max_diff)
summary(max2)

max2$cluster.vcov = cluster.vcov(max2, ~ id)
max2a = coeftest(max2, max2$cluster.vcov)
max2a

# Compare models
stargazer(max1, max2, max2a, type="text", omit = "id",
          dep.var.labels.include = FALSE,
          add.lines = list(c("Individual fixed effects?", "No", "Yes", "Yes"),
                           c("Clustered SE?", "Yes", "No", "Yes")),
          column.labels   = c("Clustered SE", "Fixed Effects", "Both"))

```

## Dealing with Attrition: Min ATE
```{r}
minstress = min(df2$stress, na.rm=TRUE) #1
maxstress = max(df2$stress, na.rm=TRUE) #5

# Max Effect, 
# control to have -4 DiD - baseline week:5, treatment: 1
# treatment to have +4 DiD - baseline week: 1, treatment 5

df2$minstress = df2$stress

# control
df2[df2$day<8 & df2$treat_code == 0,]$minstress[is.na(df2[df2$day<8 & df2$treat_code == 0,]$stress)] = maxstress
df2[df2$day>7 & df2$treat_code == 0,]$minstress[is.na(df2[df2$day>7 & df2$treat_code == 0,]$stress)] = minstress

# treatment
df2[df2$day<8 & df2$treat_code == 1,]$minstress[is.na(df2[df2$day<8 & df2$treat_code == 1,]$stress)] = minstress
df2[df2$day>7 & df2$treat_code == 1,]$minstress[is.na(df2[df2$day>7 & df2$treat_code == 1,]$stress)] = maxstress

# create rows for difference-in-difference
baseline = df2[df2$day < 8,]
treatment = df2[df2$day > 7,]
min_did = treatment$minstress - baseline$minstress

# Build dataframe with DiD as outcome only
min_diff = diff[,c(1:10, 13)]
min_diff$min_did = min_did

# distribution by treatment group
ggplot(data.frame(min_diff$min_did), aes(x=min_diff$min_did, fill = min_diff$treat)) + 
  geom_bar(position="dodge") + 
  ggtitle("Difference in Difference of Stress Levels") + 
  labs(x="Stress DiD")

# boxplot by treatment group
ggplot(data.frame(min_diff$min_did), aes(x=min_diff$treat, 
                                         y=min_diff$min_did, 
                                         fill=min_diff$treat)) + 
  geom_boxplot() + 
  ggtitle("Difference in Difference of Stress Levels by Group") + 
  labs(x="Group", y="DiD Stress")

# Difference in means 
mean(min_diff[min_diff$treat == "treatment",]$min_did) - 
  mean(min_diff[min_diff$treat == "control",]$min_did)

# max effect model ignoring clustered SEs
min1_wrong = lm(min_did ~ treat, data=min_diff)
summary(min1_wrong)

# max effect model with clustered SEs
min1_wrong$cluster.vcov = cluster.vcov(min1_wrong, ~ id)
min1 = coeftest(min1_wrong, min1_wrong$cluster.vcov)
min1

# max effect model with fixed effects by individual ID
min2 = lm(min_did ~ treat+ factor(id), data = min_diff)
summary(min2)

min2$cluster.vcov = cluster.vcov(min2, ~ id)
min2a = coeftest(min2, min2$cluster.vcov)
min2a

# Compare models
stargazer(min1, min2, min2a, type="text", omit = "id",
          dep.var.labels.include = FALSE,
          add.lines = list(c("Individual fixed effects?", "No", "Yes", "Yes"),
                           c("Clustered SE?", "Yes", "No", "Yes")),
          column.labels   = c("Clustered SE", "Fixed Effects", "Both"))

```
```{r}
point.ate <- mean(diff$did[diff$treat_code==1], na.rm=TRUE) - mean(diff$did[diff$treat_code==0], na.rm=TRUE) 
n.sims = 10e4
ri.ate <- rep(NA, n.sims)
for (i in 1:length(ri.ate)) {
  diff$ri_treat <- sample(diff$treat_code)
  ri.ate[i] <- mean(diff$did[diff$ri_treat==1], na.rm=TRUE) - mean(diff$did[diff$ri_treat==0], na.rm=TRUE)
}
hist(ri.ate, col='#66CC99')
abline(v=point.ate, col="red")
```